---
title: "Cabbages"
author: "Gil Felix"
date: "6/5/2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot

```{r}
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "", y = "VitC") +
  ggtitle("Box Plot of VitC") +
  theme(plot.title = element_text(size = 16, hjust = 0.5))
```
If you look at the w boxes on the box plot. The major box is above the lower one. The middle 50% of the method of higher is quite a bit different between the C39 and C52. They are completely apart from each other. We think we will find a statistical difference within these 2 methods.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
The average amount of Vitamin C39 is 51. The average amount of vitamin C52 is 64. 

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```
The probability of getting a result as 0.000000003405. The difference is in an extremely small number. It is not a significant difference between c39 and c52. It is possible that there is a difference, just not as significant. It does not mean it is exactly the same, so I reject the hypothesis they are the same.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Throughout this exercise I explored making a plot, making numerical result, did a t-test, and made conclusion about the data I found. I utilized R studio to make a visual representation and descriptions of my data. 
